Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-08 draft.tex
new figures for explanation results

@@

@@

			pitch fluctuation features and a terminus with three hidden layers}

@@

>>>>

		\begin{figure}
			\includegraphics[width=0.7\textwidth]{images/exp_cterm.png}
			\caption{Graphical representation of the aggregated explanation results of the best
			performing model}
			\label{figure:exp_cterm}

@@

		\begin{figure}
			\includegraphics[width=0.7\textwidth]{images/exp_mpf.png}
			\caption{Graphical representation of the aggregated explanation results of model with
			expanded pitch fluctuation features.}
			\label{figure:exp_mpf}

@@

			pitch fluctuation features and a terminus with three hidden layers.}

@@

		\begin{figure}
			\includegraphics[width=0.7\textwidth]{images/exp_mpf_cterm.png}
			\caption{Graphical representation of the aggregated explanation results of the model
			with expanded pitch fluctuation features and a terminus with three hidden layers.}
			\label{figure:exp_mpf_cterm}
